WIDS 2024 Final Project

### 2024-01-11 Code/R FIle.qmd
worked on regression model

T-test between union and non-union wages

```{r}
# 1984 to 2019
t.test(full_ntl_data$union_wage_2020_adj, full_ntl_data$nonunion_wage_2020_adj)

# 1980s
full_ntl_data_1980s <- full_ntl_data |>
  filter(year >= 1984 & year < 1990)
t.test(full_ntl_data_1980s$union_wage_2020_adj, full_ntl_data_1980s$nonunion_wage_2020_adj)

# 1990s
full_ntl_data_1990s <- full_ntl_data |>
  filter(year >= 1990 & year < 2000)
t.test(full_ntl_data_1990s$union_wage_2020_adj, full_ntl_data_1990s$nonunion_wage_2020_adj)

# 2000s
full_ntl_data_2000s <- full_ntl_data |>
  filter(year >= 2000 & year < 2010)
t.test(full_ntl_data_2000s$union_wage_2020_adj, full_ntl_data_2000s$nonunion_wage_2020_adj)

# 2010s
full_ntl_data_2010s <- full_ntl_data |>
  filter(year >= 2010 & year < 2020)
t.test(full_ntl_data_2010s$union_wage_2020_adj, full_ntl_data_2010s$nonunion_wage_2020_adj)
```

T test between median and mean incomes

```{r}
# 1984 to 2019
t.test(full_ntl_data$median_income_2020_adj, full_ntl_data$mean_income_2020_adj)

# 1980s
full_ntl_data_1980s <- full_ntl_data |>
  filter(year >= 1984 & year < 1990)
t.test(full_ntl_data_1980s$median_income_2020_adj, full_ntl_data_1980s$mean_income_2020_adj)

# 1990s
full_ntl_data_1990s <- full_ntl_data |>
  filter(year >= 1990 & year < 2000)
t.test(full_ntl_data_1990s$median_income_2020_adj, full_ntl_data_1990s$mean_income_2020_adj)

# 2000s
full_ntl_data_2000s <- full_ntl_data |>
  filter(year >= 2000 & year < 2010)
t.test(full_ntl_data_2000s$median_income_2020_adj, full_ntl_data_2000s$mean_income_2020_adj)

# 2010s
full_ntl_data_2010s <- full_ntl_data |>
  filter(year >= 2010 & year < 2020)
t.test(full_ntl_data_2010s$median_income_2020_adj, full_ntl_data_2010s$mean_income_2020_adj)
```

Regression between percent union and party state average

```{r}
# 1980s
full_state_data_1980s <- full_state_data |>
  filter(year >= 1984 & year < 1990)
CB_party_1980s_regression <- summary(lm(full_state_data_1980s$party_state_average~full_state_data_1980s$percent_collective_bargain))$coefficients

# 2010s
full_state_data_2010s <- full_state_data |>
  filter(year >= 2010 & year < 2020)
summary(lm(full_state_data_2010s$party_state_average~full_state_data_2010s$percent_union))
```

```{r}
CB_party_1980s_regression <- CB_party_1980s_regression |> 
  as_tibble() |> 
  mutate(Reggression_Run = c("Intercept", "percent_collective_bargain"))

CB_party_1980s_regression
```

>>>>

Regression between percent collective bargaining and party state average
```{r}
decade_region <- list(
  c("1980s", "Northeast"),
  c("1980s", "West"),
  c("1980s", "North Central"),
  c("1980s", "South"),
  c("2010s", "Northeast"),
  c("2010s", "West"),
  c("2010s", "North Central"),
  c("2010s", "South")
)

regression_decade_region <- function(decade1, region1) {
  full_state_data_filtered <- subset(full_state_data, regions == region1 & decade == decade1)
  model <- lm(full_state_data_filtered$party_state_average~full_state_data_filtered$percent_collective_bargain) 
  summary(model)$coefficients |> 
  as_tibble() |> 
  mutate(Reggression_Run = c("Intercept", "percent_collective_bargain"),
         Decade = c(decade1, decade1),
         Region = c(region1, region1),
         .before = Estimate)
}

full_state_data_temp <- full_state_data |>
  filter(year >= 1984 & year < 1990)
CB_party_regression <- summary(lm(full_state_data_temp$party_state_average~full_state_data_temp$percent_collective_bargain))$coefficients |> 
  as_tibble() |> 
  mutate(Reggression_Run = c("Intercept", "percent_collective_bargain"),
         Decade = c("1980s", "1980s"),
         Region = c("all", "all"),
         .before = Estimate)

for (x in decade_region) {
  CB_party_regression <- full_join(CB_party_regression, regression_decade_region(x[1], x[2]),
                                   by = join_by(Reggression_Run, Decade, Region, Estimate, `Std. Error`, `t value`, `Pr(>|t|)`))
}

full_state_data_temp <- full_state_data |>
  filter(year >= 2010 & year < 2020)
CB_party_temp <- summary(lm(full_state_data_temp$party_state_average~full_state_data_temp$percent_collective_bargain))$coefficients |> 
  as_tibble() |> 
  mutate(Reggression_Run = c("Intercept", "percent_collective_bargain"),
         Decade = c("2010s", "2010s"),
         Region = c("all", "all"),
         .before = Estimate)

CB_party_regression <- full_join(CB_party_regression, CB_party_temp,
                                   by = join_by(Reggression_Run, Decade, Region, Estimate, `Std. Error`, `t value`, `Pr(>|t|)`))

CB_party_regression |>
  filter(Reggression_Run == "percent_collective_bargain")
```
